\pdftitle

### 2018-05-18 maxNt_v3.tex
V3

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2018-05-18T10:25:17+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

The idea of the new application leads in fact to more questions. For
instance:
\begin{itemize}
\item Do the standard and new applications lead to different or contrasting
  conclusions about \enquote{cooperativity}, when applied to real data
  sets?
\item How to extend the new application when we want to study the 
  activities of individual neurons, of individual pairs, triplets, and so
  on?
\item What is the mathematical relation between the new application and
  \me\ models with hidden neurons?
\end{itemize}
Owing to space limitations we cannot investigate these questions here, but
we hope to in future work.

>>>>

%% Author: PGL  Porta Mana
%% Created: 2015-11-04T09:20:08+0100
%% Last-Updated: 2018-05-18T10:28:29+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Report-no: ***
\documentclass{article}

@@

The idea of the new application leads in fact to more questions. For
instance:
\begin{itemize}
\item Do the standard and new applications lead to different or contrasting
  conclusions about \enquote{cooperativity}, when applied to real data
  sets?
\item How to extend the new application to the \enquote{inhomogeneous} case
  \cite{schneidmanetal2006,shlensetal2006,roudietal2009b}, in which
  expectations for individual neurons or groups of neurons are constrained?
\item What is the mathematical relation between the new application and
  \me\ models with hidden neurons?
\end{itemize}
Owing to space limitations we cannot investigate these questions here, but
we hope to in future work.
